### 2015-07-08 text/ms.Rmd
More edits to intro

\noindent The estimation of ecological population status and trajectory are two
of the most fundamental values to quantify in ecological resource management
[e.g. @mace2008]. Status and trajectory are fundamental to everything from
global assessments of extinction risk [e.g. @stuart2004; @schipper2008;
@juan-jorda2011] to local management of hunting (REF) and fishing (REF). But
ecological resource managers are often faced with reconciling multiple uncertain
and potentially conflicting estimates of these quantities---some models may
suggest a population is increasing in abundance while other may suggest it is
declining (e.g. REF).

One solution is to take the average or weighted average of an ensemble of model
predictions. Such ensembles are typically more accurate and less biased than
individual model estimates and can integrate uncertainty in model structure,
initial conditions, and parameter estimation [@araujo2007]. For instance,
REF-international did this and REF-national did this.

@@

In fisheries science, a common task is estimating the status and trajectory of
an exploited fish population. For the majority of fish stocks, we have limited
fisheries independent data to estimate stock status [@fao2014]. In recent
years, a number of methods have been proposed to derive population status based
on the limited information that is broadly available: fisheries catch time
series and basic knowledge about the productivity of the species 
[e.g. @vasconcellos2005; @martell2013]. Recently, @rosenberg2014
investigated the ability for four such models to estimate population status through
a large-scale simulation experiment. A key finding was that these models
frequently disagree on population status and any one model has relatively poor
predictive ability on average (e.g. Fig. \ref{motivate}).

Here, we estimate population status and trajectory of exploited fish populations
using ensemble and superensemble models (collectively referred to 'ensemble
methods'). We explore a variety of approaches applied to both simulated and
real-world fish stocks and compare predictive performance. We find that
ensembles, and in particular superensembles, generally improved predictive
performance of status and trajectory of fish populations over any single
model---especially when considered across multiple dimensions of predictive
ability and across multiple datasets. Furthermore, the output from
superensembles can aid mechanistic understanding of how individual models of
status and trajectory perform.

>>>>

\noindent Ecological population status and trajectory are two of the most
fundamental values to quantify in ecological resource management [e.g.
@mace2008]. Population status and trajectory are key to everything from global
assessments of extinction risk [e.g. @stuart2004; @schipper2008;
@juan-jorda2011] to local management of hunting (REF) and fishing (REF). But
ecological resource managers are often faced with reconciling multiple
uncertain and potentially conflicting estimates of these quantities---some
models may suggest a population is at risk and declining in abundance while
others may suggest it is not at risk and stable (e.g. REF).

One solution is to take the average or weighted average of an ensemble of model
predictions. Such ensembles are typically more accurate and less biased than
individual model estimates and can integrate uncertainty in model structure,
initial conditions, and parameter estimation [@araujo2007]. For instance,
REF-international did this and REF-national did this...

@@

In fisheries science, a number of models have been proposed to assess
population status (biomass compared to biomass at maximum sustainable yield,
$B/B_\mathrm{MSY}$) and trajectory based on the limited data available for the
majority of stocks: catches and a basic understanding of population
productivity [e.g. @vasconcellos2005; @martell2013]. Recently, @rosenberg2014
investigated the performance of four such models through a large-scale
simulation experiment. The four models frequently disagreed about population
status and any one model had relatively poor predictive ability on average
(e.g. Fig. \ref{motivate}).

Here, we estimate population status and trajectory of exploited fish
populations using ensembles and superensembles (collectively 'ensemble
methods') of these four data-limited models. We explore a variety of approaches
applied to both simulated and real-world fish stocks and compare predictive
performance. We find that ensembles, and in particular superensembles,
generally improved predictive performance of status and trajectory of fish
populations over any single model---especially when considered across multiple
dimensions of predictive ability and across multiple datasets. Furthermore, the
output from superensembles can aid mechanistic understanding of how individual
models of status and trajectory perform.
